<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{Examples from the googleVis package}
-->
# Using Roles via googleVis

Add the ability to pass columns roles for further processing downstream.

Role columns must follow column they pertain to.  Proper naming
conventions must be be observed.  For example, roles fulfilling tooltip
roles and must be called "foo.blah.tooltip".

For more details see the [Google documentation](https://developers.google.com/chart/interactive/docs/roles).

The following examples should help to illustrate the concept. 

```{r setOptions, message=FALSE, echo=FALSE}
library(googleVis)
op <- options(gvis.plot.tag='chart')
read_chunk('../demo/Roles.R')
```
The first example uses a data set that has the additional column
`pop.html.tooltip` with the first 11 letters of the latin alphabet.
This column is mapped automatically as a tooltip, when the user hovers 
over the chart point.
```{r Tooltip, results='asis', tidy=FALSE}
```

```{r TooltipHTML, results='asis', tidy=FALSE}
```

```{r CertaintyScopeEmphasis, results='asis', tidy=FALSE}
```

```{r ColumnChart, results='asis', tidy=FALSE}
```

```{r LimitData, results='asis', tidy=FALSE}
```

```{r TwoLines, results='asis', tidy=FALSE}
```
