<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{Markdown example with knitr and googleVis}
-->
# Markdown example with knitr and googleVis
===========================================
This is a little Markdown example file.
Set the googleVis options first.
In this case change the behaviour of plot.gvis
```{r setOptions, message=FALSE}
library(googleVis)
op <- options(gvis.plot.tag='chart')
```
The following plot statements will automatically return  the HTML
required for the 'knitted' output. 

## Combo chart
```{r ComboExample, results='asis', tidy=FALSE}
## Add the mean
CityPopularity$Mean=mean(CityPopularity$Popularity)
CC <- gvisComboChart(CityPopularity, xvar='City',
          yvar=c('Mean', 'Popularity'),
          options=list(seriesType='bars',
                       width=450, height=300,
                       title='City Popularity',
                       series='{0: {type:\"line\"}}'))
plot(CC)
```
Example of gvisComboChart with R code shown above.

## Place two charts next to each other
```{r gvisMergeExample, results='asis', echo=FALSE}
Geo <- gvisGeoChart(Exports, locationvar='Country', colorvar='Profit', 
                    options=list(height=300, width=350)) 
Tbl <- gvisTable(Exports, options=list(height=300, width=200))
plot(gvisMerge(Geo, Tbl, horizontal=TRUE))
``````
Example of a gvisGeoChart with gvisTable and R code hidden.

## Motion Chart
```{r MotionChartExample, results='asis', tidy=FALSE}
M <- gvisMotionChart(Fruits, 'Fruit', 'Year',
         options=list(width=400, height=350))
plot(M)
```
Please note that the Motion Chart is only displayed when hosted on a
web server, or is placed in a directory which has been added to the 
trusted sources in the [security settings of Macromedia]
(http://www.macromedia.com/support/documentation/en/flashplayer/help/settings_manager04.html). 
See the googleVis package vignette for more details. 

```{r resetOptions}
## Set options back to original options
options(op)
```
