<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{Using Roles via googleVis}
-->
# Using Roles via googleVis

Roles add the ability to pass columns for further processing downstream. Role columns must follow column they pertain to. Proper naming
conventions must be be observed. For example, roles fulfilling tooltip
roles and must be called "foo.blah.tooltip". For more details see the [Google documentation](https://developers.google.com/chart/interactive/docs/roles).

The following examples should help to illustrate the concept. 

```{r setOptions, message=FALSE, echo=FALSE}
library(googleVis)
library(knitr)
op <- options(gvis.plot.tag='chart')
read_demo('Roles', 'googleVis')
```
The first example uses a data set that has the additional column
`pop.html.tooltip` with the first 11 letters of the Latin alphabet.
This column is mapped automatically as a tooltip, when the user hovers 
over the chart point.
```{r Tooltip, results='asis', tidy=FALSE}
```
I can embed some HTML code into my tooltip as well, but then I have to
set this in my options list as well.
```{r TooltipHTML, results='asis', tidy=FALSE}
```
Often it is helpful to highlight certain parts of my data, e.g.
subsets that I feel more certain about or that I want to emphasize for 
other reasons the reader. 
In a similar way as above I add additional columns to by data
and asign boolean values to indicate which values I'd like to highlight.
```{r CertaintyScopeEmphasis, results='asis', tidy=FALSE}
```

Using roles with column or bar charts has its some specifics.
Instead of emphasize, I can use style to change the colors.
```{r ColumnChart, results='asis', tidy=FALSE}
```

```{r LimitData, results='asis', tidy=FALSE}
```

```{r TwoLines, results='asis', tidy=FALSE}
```

Setting the annotations style to line allows me to add little reference lines
to the plot.
```{r VerticalReferenceLine, results='asis', tidy=FALSE}
```
